\sc Building sex-specific synthetic lethality network in cancer - Temp Name

### 2023-08-10 sl_report_pmcrc/paper0904.tex
updates

	We also verified the statistical significance of the difference between normal and tumor tissue expression across all cancer types and within each cancer type using a non-parametric multivariate analysis of variance (NPMANOVA), also known as a permutational multivariate analysis of variance (PERMANOVA).

>>>>

	We also verified the statistical significance of the difference between normal and tumor tissue expression across all cancer types and within each cancer type using a non-parametric multivariate analysis of variance (NPMANOVA), also known as a permutational multivariate analysis of variance (PERMANOVA). This is a nonparametric test used to compare multivariate distributions of several groups and the null hypothesis for this test is that the centroids of all groups are equal \citep{anderson2005permutational}. In the case of this study, a low p-value indicates a significant difference in the centroids between normal tissue and tumor tissue. We did not have time to produce PCA plots that showed the centroids, but it would be beneficial to produce these plots in the future. We also did not perform an analysis that could identify the variance among the clusters so we could not statistically test if there was more heterogeneity among tumor tissue samples compared to normal tissue samples.
